Localisation and Sensor Privacy Using the Extended Information Filter and Secure Partially Homomorphic Aggregation

### 2020-07-08 main.tex
Gitignore
Started on structure and intro substructure Current intro substructure is shit - WIP Added ISAS macros and bibtex files

%=================================================================
\documentclass[journal,article,submit,moreauthors,pdftex]{Definitions/mdpi}

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}

% Authors, for metadata in PDF
\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation 3} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}
The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions for authors page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX related questions please contact latex@mdpi.com.
%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

>>>>

%=================================================================
\documentclass[sensors,article,submit,moreauthors,pdftex]{Definitions/mdpi}

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Localisation and Sensor Privacy Using the Extended Information Filter and Secure Partially Homomorphic Aggregation}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-9581-9937} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0001-8996-5738} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0001-9870-2331} % Add \orcidC{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Marko Ristic $^{1}$\orcidA{}, Benjamin Noack $^{1}$\orcidB{} and Uwe D. Hanebeck $^{1,}$*\orcidC{}}

% Authors, for metadata in PDF
\AuthorNames{Marko Ristic, Benjamin Noack and Uwe D. Hanebeck}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address[1]{%
$^{1}$ \quad Intelligent Sensor-Actuator-systems Laboratory, Institute for Anthropomatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany; marko.ristic@kit.edu; noack@kit.edu; uwe.hanebeck@kit.edu}

% Contact information of the corresponding author
\corres{Correspondence: uwe.hanebeck@kit.edu; Tel.: +49-721-608-43909}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
Introduce localisation, filtering and the need for privacy.

Examples of environments where privacy is relevant and concrete examples where lack of privacy could have large costs

Explain the additional difficulties with achieving privacy in distributed environments (malicious subsets etc). AO and pWSAO.

Public key cryptography applicability to distributed systems; difference to symmetric schemes. Homomorphic encryption power and use case.

Differential privacy concerned with hiding individuals in a group but results in noisy results. Also often requires a trusted aggregator, although aggregation methods exist.

Application of partially Homomorphic encryption. Control examples include Alexandru and Farokhi papers, mostly applicable due to distributed aggregation step.

Estimation examples include Filters with a sensor hierarchy and linear models, localisation methods which hide sensor information in a model-free environment but either pay in security or require additional rounds of communication.

Additionally encoding for signal processing is an issue. Typically unlimited scalar multiplications and additions using a scheme that allows it over integers does not work on encoded real numbers. Google bignum adds power but risks overflow and leaks exponents, Farokhi leaks no information but allows only a single multiplication.

Describe Navigator scenario and our contributions

Section Summary

\section{Problem Statement}
Restate the scenario but more formally.

Exact security guarantees we aim for

Rough computational capabilities expected by parties

Fixed sensor subsets of which only whole subsets can be used at once

\section{Existing Literature}

Details and differences to private localisation methods, aggregation methods, and encoding methods

Model-free localisation examples can include polygon thing, WSN examples which protect against adversaries but don't preserve individual information. Importantly model-based filtering and localisation provides accurate estimates and these are not applicable there.

Estimation examples can include Aristov paper (which requires linear model, and a hierarchy of sensors)

Alexandru weighted aggregation requires redistributing keys at every timestep resulting in a costly operations, and a complicated communication protocol.

Encoding of signal processing values for use in encrypted processing should consist of google bignum library and Farokhi qnm encoding

\section{Preliminaries}

\subsection{Integer Encoding for Real Numbers}
\subsection{Paillier Encryption Scheme}
\subsection{Joye-Libert Privacy-Preserving Aggregation}
\subsection{Extended Information Filter}

\section{Private Partially Homomorphic Aggregation}
\section{Requirements for Measurement Model}
\section{Localisation Measurement Modification}

\section{Private Localisation with Privacy-Preserving Sensors}

\section{Results}
\section{Conclusion}

<Rest is template>

\section{How to Use this Template}
The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions for authors page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX related questions please contact latex@mdpi.com.
%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
